HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-13 scnn.tex
appendix: spherical harmonics

    \item (TK) make the bibliography display only a few name
    % \item (yes) Michael, do you agree with the title HealpixNet? I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix. Hence I now agree with the title. Feel free to edit. Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
    % \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
    \item (TK) add info on comparison with histograms, so that it's just a demonstration
    % \item Finish section on Convolutions on graphs (Michael - Nathanael)
    % \item finish section on Efficient convolutions (Michael)
    % \item (done) Plot of the new filters from Mass maps
    % \item (done!, plot to be added) check the power spectrum after smoothing
    % \item (done!) upgrade the plot of pooling (Nathanael)
    \item (TK) possibly improve plot of pooling
	% \item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
    \item (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) Figure 1 to be round
    \item (first version done) conclusions
    % \item (done!) new simulations with 3 arcmin smoothing
    % \item (done!) simulation with cross-validation for the histogram
    % \item (done!) Update result section according to the new simulations...
    % \item (done!) simulation PSD
    % \item (done!) Results figure, add sigma8
    % \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
    \item Should the heat example go to appendix
    \item TK read the heat section again
    \item TK read the result section
    \item TK check the appendix
    \item TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item TK read everything
\end{itemize}

@@

\section{Spherical harmonics VS graph Fourier eigenvectors}
\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
graph Fourier basis used for the convolution. While there is a clear
resemblance with the spherical harmonic, the small irregularities in the
sampling (see \figref{healpix_graph_4}) have an effect on the
graph Fourier eigenvectors. First, conterintuitively, some graph eigenvectors will be
localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
of the sphere.  Second, as Nside increase toward infinity and hence the number
of pixels $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
converge toward the spherical harmonics. We believe that it might be the case
for a different graph construction (fully connected) and that a proof could be
built on top of the work of~\cite{belkin2007convergence}. This is obviously
out of the scope of this contribution.

>>>>

    \item (TK) make the bibliography display only a few name
    % \item (yes) Michael, do you agree with the title HealpixNet? I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix. Hence I now agree with the title. Feel free to edit. Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
    % \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
    \item (TK) add info on comparison with histograms, so that it's just a demonstration
    % \item Finish section on Convolutions on graphs (Michael - Nathanael)
    % \item finish section on Efficient convolutions (Michael)
    % \item (done) Plot of the new filters from Mass maps
    % \item (done!, plot to be added) check the power spectrum after smoothing
    % \item (done!) upgrade the plot of pooling (Nathanael)
    \item (TK) possibly improve plot of pooling
	% \item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
    \item (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) Figure 1 to be round
    \item (first version done) conclusions
    % \item (done!) new simulations with 3 arcmin smoothing
    % \item (done!) simulation with cross-validation for the histogram
    % \item (done!) Update result section according to the new simulations...
    % \item (done!) simulation PSD
    % \item (done!) Results figure, add sigma8
    % \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
    \item Should the heat example go to appendix
    \item TK read the heat section again
    \item TK read the result section
    \item TK check the appendix
    \item TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item TK read everything
	\item MD should we keep those small appendices rather than merging them in the main text?
\end{itemize}

@@

\section{Graph Fourier eigenvectors and spherical harmonics}

The first 16 eigenvectors of the graph graph Laplacian, forming the graph Fourier basis, are shown in \figref{graph_harmonics}. While there is a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
First, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
Second, as the resolution is increased with $N_{side} \rightarrow \infty$ and $N_{pix} \rightarrow \infty$, we are still unsure if the eigenvectors would converge towards the spherical harmonics. We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of~\cite{belkin2007convergence}. That is however out of the scope of this contribution.
